Comparisons in three center

### 2020-12-13 scripts/43_comparisons_3.Rmd
udpate

pcts <- sub_phenos %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x))) 
```

>>>>

pcts <- sub_phenos %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann2/{.y}_pcts.tsv'))) 
```

```{r}
fns <- list.files('../data/shotgun_output/humann2/', pattern = '_lefse_ready.tsv')

cmds <- tibble(
  fns = fns
) %>% 
  transmute(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300')) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann2/lefse_cmd.sh', col_names = F)
cmds

```
